ABM simulating short-term mating behaviors

### 2022-06-01 submission/manuscript.Rmd
added texts for the in-pool number difference and stats tests

@@

The results from Experiment 1 showed that when there were gender differences in preferences for short-term mating, there was no gender difference in the average number of short-term mating experiences among heterosexual individuals (*M~men~* = `r m_exp_all.mean_011`, *SD~men~* = `r m_exp_all.sd_011`; *M~women~* = `r f_exp_all.mean_011`, *SD~women~* = `r f_exp_all.sd_011`), Cohen's *d* = `r exp_all.d_011`. Nor was there a difference in the average number of short-term mates (*M~men~* = `r m_partner_all.mean_011`, *SD~men~* = `r m_partner_all.sd_011`; *M~women~* = `r f_partner_all.mean_011`, *SD~women~* = `r f_partner_all.sd_011`), Cohen's *d* = `r partner_all.d_011` (Figure 1).

\begin{figure}[h]
  \centering
  \includegraphics[width=100mm]{figures/fig1_men_vs_women.pdf}
  \caption{\textbf{Short-term mating behaviors of men and women after 1,000 time steps in the model when gender differences existed in mating preferences.} Violin plots summarizing the outcome variables separately for heterosexual individuals and gay men and lesbian women. Plot (A) shows the average number of short-term mating experiences, and plot (B) shows the average number of short-term mates. Central points show mean values and whiskers represent standard errors, but the standard errors are small and overlap to form a single bar. The averages were calculated using the full population of men and women in the model (\textit{N\textsubscript{men}} = \textit{N\textsubscript{women}} = 150).}
\end{figure}

@@

The results from Experiment 2 showed that when there were gender differences in preferences for short-term mating, there were gender differences in short-term mating behaviors between gay men and lesbian women (Figure 1). The average number of short-term mating experiences was higher among gay men (*M* = `r m_exp_all.mean_111`, *SD* = `r m_exp_all.sd_111`) than among lesbian women (*M* = `r f_exp_all.mean_111`, *SD* = `r f_exp_all.sd_111`), *t*(`r exp.all.parameter_111`) = `r exp.all.statistic_111`, *p* `r exp.all.p.value_111`, Cohen's *d* = `r exp_all.d_111`. Similarly, the average number of short-term mates was higher among gay men (*M* = `r m_partner_all.mean_111`, *SD* = `r m_partner_all.sd_111`) than among lesbian women (*M* = `r f_partner_all.mean_111`, *SD* = `r f_partner_all.sd_111`), *t*(`r partner.all.parameter_111`) = `r partner.all.statistic_111`, *p* `r partner.all.p.value_111`, Cohen's *d* = `r partner_all.d_111`.

@@

```{r sec2.2}
# the number of experiences, difference*2, heterosexual in the mating pool
m_exp_ip.mean_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(m_exp_ip.mean)
m_exp_ip.sd_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(m_exp_ip.sd)
f_exp_ip.mean_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(f_exp_ip.mean)
f_exp_ip.sd_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(f_exp_ip.sd)
exp_ip.parameter_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(exp_ip.parameter)
exp_ip.statistic_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(exp_ip.statistic)
exp_ip.p.value_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(exp_ip.p.value)
exp_ip.d_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(exp_ip.d) %>% abs()

# the number of partners, difference*2, heterosexual in the mating pool
m_partner_ip.mean_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(m_partner_ip.mean)
m_partner_ip.sd_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(m_partner_ip.sd)
f_partner_ip.mean_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(f_partner_ip.mean)
f_partner_ip.sd_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(f_partner_ip.sd)
partner_ip.parameter_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(partner_ip.parameter)
partner_ip.statistic_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(partner_ip.statistic)
partner_ip.p.value_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(partner_ip.p.value)
partner_ip.d_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(partner_ip.d) %>% abs()

# the number of in-pool, difference*2
m_inpool.mean_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(m_inpool.mean)
m_inpool.sd_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(m_inpool.sd)
f_inpool.mean_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(f_inpool.mean)
f_inpool.sd_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(f_inpool.sd)
```

In Experiment 1, however, when the means of the outcome variables were calculated only among men and women in the mating pool (the number of individuals in the mating pool: *M~men~* = `r m_inpool.mean_011`, *SD~men~* = `r m_inpool.sd_011`; *M~women~* = `r f_inpool.mean_011`, *SD~women~* = `r f_inpool.sd_011`), there were gender differences in short-term mating behaviors when men and women had differential preferences for short-term mating. The average number of short-term mating experiences was higher among heterosexual men (*M* = `r m_exp_ip.mean_011`, *SD* = `r m_exp_ip.sd_011`) than among heterosexual women (*M* = `r f_exp_ip.mean_011`, *SD* = `r f_exp_ip.sd_011`), *t*(`r exp_ip.parameter_011`) = `r exp_ip.statistic_011`, *p* `r exp_ip.p.value_011`, Cohen's *d* = `r exp_ip.d_011`. Likewise, the average number of short-term mates was higher among heterosexual men (*M* = `r m_partner_ip.mean_011`, *SD* = `r m_partner_ip.sd_011`) than among heterosexual women (*M* = `r f_partner_ip.mean_011`, *SD* = `r f_partner_ip.sd_011`), *t*(`r partner_ip.parameter_011`) = `r partner_ip.statistic_011`, *p* `r partner_ip.p.value_011`, Cohen's *d* = `r partner_ip.d_011`.

@@

```{r sec2}
# the number of experiences, difference*2, heterosexual and gay men
m_exp_all.mean_0_11 <-
  results_hg %>% filter(ls == "1_1") %>% pull(m_exp_all.mean_0)
m_exp_all.sd_0_11 <-
  results_hg %>% filter(ls == "1_1") %>% pull(m_exp_all.sd_0)
m_exp_all.mean_1_11 <-
  results_hg %>% filter(ls == "1_1") %>% pull(m_exp_all.mean_1)
m_exp_all.sd_1_11 <-
  results_hg %>% filter(ls == "1_1") %>% pull(m_exp_all.sd_1)
exp.all.parameter_hg <-
  results_hg %>% filter(ls == "1_1") %>% pull(m_exp_all.parameter)
exp.all.statistic_hg <-
  results_hg %>% filter(ls == "1_1") %>% pull(m_exp_all.statistic)
exp.all.p.value_hg <-
  results_hg %>% filter(ls == "1_1") %>% pull(m_exp_all.p.value)
exp_all.d_hg <-
  results_hg %>% filter(ls == "1_1") %>% pull(m_exp_all.d) %>% abs()

@@

Gay men engaged in short-term mating behaviors more than heterosexual men did (Figure 2). The average number of short-term mating experiences (as calculated using the full population of men) was higher among gay men (*M* = `r m_exp_all.mean_1_11`, *SD* = `r m_exp_all.sd_1_11`) than among heterosexual men (*M* = `r m_exp_all.mean_0_11`, *SD* = `r m_exp_all.sd_0_11`), *t*(`r exp.all.parameter_hg`) = `r exp.all.statistic_hg`, *p* `r exp.all.p.value_hg`, Cohen's *d* = `r exp_all.d_hg`. Similarly, the average number of short-term mates (as calculated using the full population of men) was higher among gay men (*M* = `r m_partner_all.mean_1_11`, *SD* = `r m_partner_all.sd_1_11`) than among heterosexual men (*M* = `r m_partner_all.mean_0_11`, *SD* = `r m_partner_all.sd_0_11`), *t*(`r partner.all.parameter_hg`) = `r partner.all.statistic_hg`, *p* `r partner.all.p.value_hg`, Cohen's *d* = `r partner_all.d_hg`.

\begin{figure}[h]
  \centering
  \includegraphics[width=0.8\columnwidth]{figures/fig2_hetero_vs_gay_men.pdf}
  \caption{\textbf{Short-term mating behaviors of heterosexual and gay men after 1,000 time steps in the model when gender differences existed in mating preferences.} Violin plots summarizing the outcome variables. Plot (A) shows the average number of short-term mating experiences, and plot (B) shows the average number of short-term mates. Central points show mean values and whiskers represent standard errors, but the standard errors are small and overlap to form a single bar. The averages were calculated using the full population of heterosexual and gay men in the model (\textit{N\textsubscript{hetero}} = \textit{N\textsubscript{gay}} = 150).}
\end{figure}

@@

```{r sec3.1}
# the number of experiences, difference in standard, heterosexual
m_exp_ip.mean_001 <-
  results %>% filter(hls == "0_0_1") %>% pull(m_exp_ip.mean)
m_exp_ip.sd_001 <-
  results %>% filter(hls == "0_0_1") %>% pull(m_exp_ip.sd)
f_exp_ip.mean_001 <-
  results %>% filter(hls == "0_0_1") %>% pull(f_exp_ip.mean)
f_exp_ip.sd_001 <-
  results %>% filter(hls == "0_0_1") %>% pull(f_exp_ip.sd)
exp_ip.d_001 <-
  results %>% filter(hls == "0_0_1") %>% pull(exp_ip.d) %>% abs()

@@

```{r sec3.2}
# the number of experiences, difference in likelihood, gay and lesbian
m_exp_all.mean_110 <-
  results %>% filter(hls == "1_1_0") %>% pull(m_exp_all.mean)
m_exp_all.sd_110 <-
  results %>% filter(hls == "1_1_0") %>% pull(m_exp_all.sd)
f_exp_all.mean_110 <-
  results %>% filter(hls == "1_1_0") %>% pull(f_exp_all.mean)
f_exp_all.sd_110 <-
  results %>% filter(hls == "1_1_0") %>% pull(f_exp_all.sd)
exp_all.d_110 <-
  results %>% filter(hls == "1_1_0") %>% pull(exp_all.d) %>% abs()

>>>>

N <- 150

@@

The results from Experiment 1 showed that when there were gender differences in preferences for short-term mating, there was no gender difference in the average number of short-term mating experiences among the full population of heterosexual individuals (*M~men~* = `r m_exp_all.mean_011`, *SD~men~* = `r m_exp_all.sd_011`; *M~women~* = `r f_exp_all.mean_011`, *SD~women~* = `r f_exp_all.sd_011`), Cohen's *d* = `r exp_all.d_011`. Nor was there a difference in the average number of short-term mates (*M~men~* = `r m_partner_all.mean_011`, *SD~men~* = `r m_partner_all.sd_011`; *M~women~* = `r f_partner_all.mean_011`, *SD~women~* = `r f_partner_all.sd_011`), Cohen's *d* = `r partner_all.d_011` (Figure \ref{fig:men_vs_women}).

\begin{figure}[h]
  \centering
  \includegraphics[width=100mm]{figures/fig1_men_vs_women.pdf}
  \caption{\textbf{Short-term mating behaviors of men and women after 1,000 time steps in the model when gender differences existed in mating preferences.} Violin plots summarizing the outcome variables separately for heterosexual individuals and gay men and lesbian women. Plot (A) shows the average number of short-term mating experiences, and plot (B) shows the average number of short-term mates. Central points show mean values and whiskers represent standard errors, but the standard errors are small and overlap to form a single bar. The averages were calculated using the full population of men and women in the model (\textit{N\textsubscript{men}} = \textit{N\textsubscript{women}} = 150).}
  \label{fig:men_vs_women}
\end{figure}

@@

The results from Experiment 2 showed that when there were gender differences in preferences for short-term mating, there were gender differences in short-term mating behaviors between gay men and lesbian women (Figure \ref{fig:men_vs_women}). The average number of short-term mating experiences was higher among gay men (*M* = `r m_exp_all.mean_111`, *SD* = `r m_exp_all.sd_111`) than among lesbian women (*M* = `r f_exp_all.mean_111`, *SD* = `r f_exp_all.sd_111`), *t*(`r exp.all.parameter_111`) = `r exp.all.statistic_111`, *p* `r exp.all.p.value_111`, Cohen's *d* = `r exp_all.d_111`. Similarly, the average number of short-term mates was higher among gay men (*M* = `r m_partner_all.mean_111`, *SD* = `r m_partner_all.sd_111`) than among lesbian women (*M* = `r f_partner_all.mean_111`, *SD* = `r f_partner_all.sd_111`), *t*(`r partner.all.parameter_111`) = `r partner.all.statistic_111`, *p* `r partner.all.p.value_111`, Cohen's *d* = `r partner_all.d_111`.

@@

```{r sec2}
# the number of in-pool, difference*2
m_inpool.mean_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(m_inpool.mean)
m_inpool.sd_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(m_inpool.sd)
f_inpool.mean_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(f_inpool.mean)
f_inpool.sd_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(f_inpool.sd)
inpool.parameter_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(inpool.parameter)
inpool.statistic_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(inpool.statistic)
inpool.p.value_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(inpool.p.value)
inpool.d_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(inpool.d) %>% abs()

# the number of experiences, difference*2, heterosexual in the mating pool
m_exp_ip.mean_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(m_exp_ip.mean)
m_exp_ip.sd_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(m_exp_ip.sd)
f_exp_ip.mean_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(f_exp_ip.mean)
f_exp_ip.sd_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(f_exp_ip.sd)
exp_ip.parameter_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(exp_ip.parameter)
exp_ip.statistic_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(exp_ip.statistic)
exp_ip.p.value_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(exp_ip.p.value)
exp_ip.d_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(exp_ip.d) %>% abs()

# the number of partners, difference*2, heterosexual in the mating pool
m_partner_ip.mean_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(m_partner_ip.mean)
m_partner_ip.sd_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(m_partner_ip.sd)
f_partner_ip.mean_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(f_partner_ip.mean)
f_partner_ip.sd_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(f_partner_ip.sd)
partner_ip.parameter_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(partner_ip.parameter)
partner_ip.statistic_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(partner_ip.statistic)
partner_ip.p.value_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(partner_ip.p.value)
partner_ip.d_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(partner_ip.d) %>% abs()
```

In Experiment 1, there was a smaller proportion of heterosexual men in the mating pool (*M* = `r m_inpool.mean_011/N`, *SD* = `r m_inpool.sd_011/N`) compared to women (*M* = `r f_inpool.mean_011/N`, *SD* = `r f_inpool.sd_011/N`)), *t*(`r inpool.parameter_011`) = `r inpool.statistic_011`, *p* `r inpool.p.value_011`, Cohen's *d* = `r inpool.d_011`. In this population, there were gender differences in short-term mating behaviors when men and women had differential preferences for short-term mating (Figure **x**). The average number of short-term mating experiences was higher among heterosexual men (*M* = `r m_exp_ip.mean_011`, *SD* = `r m_exp_ip.sd_011`) than among heterosexual women (*M* = `r f_exp_ip.mean_011`, *SD* = `r f_exp_ip.sd_011`), *t*(`r exp_ip.parameter_011`) = `r exp_ip.statistic_011`, *p* `r exp_ip.p.value_011`, Cohen's *d* = `r exp_ip.d_011`. Likewise, the average number of short-term mates was higher among heterosexual men (*M* = `r m_partner_ip.mean_011`, *SD* = `r m_partner_ip.sd_011`) than among heterosexual women (*M* = `r f_partner_ip.mean_011`, *SD* = `r f_partner_ip.sd_011`), *t*(`r partner_ip.parameter_011`) = `r partner_ip.statistic_011`, *p* `r partner_ip.p.value_011`, Cohen's *d* = `r partner_ip.d_011`.

@@

```{r sec3}
# the number of experiences, difference*2, heterosexual and gay men
m_exp_all.mean_0_11 <-
  results_hg %>% filter(ls == "1_1") %>% pull(m_exp_all.mean_0)
m_exp_all.sd_0_11 <-
  results_hg %>% filter(ls == "1_1") %>% pull(m_exp_all.sd_0)
m_exp_all.mean_1_11 <-
  results_hg %>% filter(ls == "1_1") %>% pull(m_exp_all.mean_1)
m_exp_all.sd_1_11 <-
  results_hg %>% filter(ls == "1_1") %>% pull(m_exp_all.sd_1)
exp.all.parameter_hg <-
  results_hg %>% filter(ls == "1_1") %>% pull(m_exp_all.parameter)
exp.all.statistic_hg <-
  results_hg %>% filter(ls == "1_1") %>% pull(m_exp_all.statistic)
exp.all.p.value_hg <-
  results_hg %>% filter(ls == "1_1") %>% pull(m_exp_all.p.value)
exp_all.d_hg <-
  results_hg %>% filter(ls == "1_1") %>% pull(m_exp_all.d) %>% abs()

@@

Gay men engaged in short-term mating behaviors more than heterosexual men did (Figure \ref{fig:hetero_vs_gay}). The average number of short-term mating experiences (as calculated using the full population of men) was higher among gay men (*M* = `r m_exp_all.mean_1_11`, *SD* = `r m_exp_all.sd_1_11`) than among heterosexual men (*M* = `r m_exp_all.mean_0_11`, *SD* = `r m_exp_all.sd_0_11`), *t*(`r exp.all.parameter_hg`) = `r exp.all.statistic_hg`, *p* `r exp.all.p.value_hg`, Cohen's *d* = `r exp_all.d_hg`. Similarly, the average number of short-term mates (as calculated using the full population of men) was higher among gay men (*M* = `r m_partner_all.mean_1_11`, *SD* = `r m_partner_all.sd_1_11`) than among heterosexual men (*M* = `r m_partner_all.mean_0_11`, *SD* = `r m_partner_all.sd_0_11`), *t*(`r partner.all.parameter_hg`) = `r partner.all.statistic_hg`, *p* `r partner.all.p.value_hg`, Cohen's *d* = `r partner_all.d_hg`.

\begin{figure}[h]
  \centering
  \includegraphics[width=0.8\columnwidth]{figures/fig3_hetero_vs_gay_men.pdf}
  \caption{\textbf{Short-term mating behaviors of heterosexual and gay men after 1,000 time steps in the model when gender differences existed in mating preferences.} Violin plots summarizing the outcome variables. Plot (A) shows the average number of short-term mating experiences, and plot (B) shows the average number of short-term mates. Central points show mean values and whiskers represent standard errors, but the standard errors are small and overlap to form a single bar. The averages were calculated using the full population of heterosexual and gay men in the model (\textit{N\textsubscript{hetero}} = \textit{N\textsubscript{gay}} = 150).}
  \label{fig:hetero_vs_gay}
\end{figure}

@@

```{r sec4.1}
# the number of experiences, difference in standard, heterosexual
m_exp_ip.mean_001 <-
  results %>% filter(hls == "0_0_1") %>% pull(m_exp_ip.mean)
m_exp_ip.sd_001 <-
  results %>% filter(hls == "0_0_1") %>% pull(m_exp_ip.sd)
f_exp_ip.mean_001 <-
  results %>% filter(hls == "0_0_1") %>% pull(f_exp_ip.mean)
f_exp_ip.sd_001 <-
  results %>% filter(hls == "0_0_1") %>% pull(f_exp_ip.sd)
exp_ip.d_001 <-
  results %>% filter(hls == "0_0_1") %>% pull(exp_ip.d) %>% abs()

@@

```{r sec4.2}
# the number of experiences, difference in likelihood, gay and lesbian
m_exp_all.mean_110 <-
  results %>% filter(hls == "1_1_0") %>% pull(m_exp_all.mean)
m_exp_all.sd_110 <-
  results %>% filter(hls == "1_1_0") %>% pull(m_exp_all.sd)
f_exp_all.mean_110 <-
  results %>% filter(hls == "1_1_0") %>% pull(f_exp_all.mean)
f_exp_all.sd_110 <-
  results %>% filter(hls == "1_1_0") %>% pull(f_exp_all.sd)
exp_all.d_110 <-
  results %>% filter(hls == "1_1_0") %>% pull(exp_all.d) %>% abs()

### 2022-06-01 submission/manuscript.tex
added texts for the in-pool number difference and stats tests

The results from Experiment 1 showed that when there were gender
differences in preferences for short-term mating, there was no gender
difference in the average number of short-term mating experiences among
heterosexual individuals (\emph{M\textsubscript{men}} = 1.43,
\emph{SD\textsubscript{men}} = 0.24; \emph{M\textsubscript{women}} =
1.43, \emph{SD\textsubscript{women}} = 0.24), Cohen's \emph{d} = 0.00.
Nor was there a difference in the average number of short-term mates
(\emph{M\textsubscript{men}} = 0.80, \emph{SD\textsubscript{men}} =
0.11; \emph{M\textsubscript{w}} = 0.80, \emph{SD\textsubscript{women}} =
0.11), Cohen's \emph{d} = 0.00 (Figure 1).

\begin{figure}[h]
  \centering
  \includegraphics[width=100mm]{figures/fig1_men_vs_women.pdf}
  \caption{\textbf{Short-term mating behaviors of men and women after 1,000 time steps in the model when gender differences existed in mating preferences.} Violin plots summarizing the outcome variables separately for heterosexual individuals and gay men and lesbian women. Plot (A) shows the average number of short-term mating experiences, and plot (B) shows the average number of short-term mates. Central points show mean values and whiskers represent standard errors, but the standard errors are small and overlap to form a single bar. The averages were calculated using the full population of men and women in the model (\textit{N\textsubscript{men}} = \textit{N\textsubscript{women}} = 150).}
\end{figure}

The results from Experiment 2 showed that when there were gender
differences in preferences for short-term mating, there were gender
differences in short-term mating behaviors between gay men and lesbian
women (Figure 1). The average number of short-term mating experiences
was higher among gay men (\emph{M} = 2.63, \emph{SD} = 0.37) than among
lesbian women (\emph{M} = 0.32, \emph{SD} = 0.10), \emph{t}(4,998) =
-301.78, \emph{p} \textless{} .001, Cohen's \emph{d} = 8.54. Similarly,
the average number of short-term mates was higher among gay men
(\emph{M} = 1.72, \emph{SD} = 0.19) than among lesbian women (\emph{M} =
0.25, \emph{SD} = 0.07), \emph{t}(4,998) = -357.69, \emph{p} \textless{}
.001, Cohen's \emph{d} = 10.12.

@@

In Experiment 1, however, when the means of the outcome variables were
calculated only among men and women in the mating pool (the number of
individuals in the mating pool: \emph{M\textsubscript{men}} = 56.85,
\emph{SD\textsubscript{men}} = 5.99; \emph{M\textsubscript{women}} =
77.04, \emph{SD\textsubscript{women}} = 7.53), there were gender
differences in short-term mating behaviors when men and women had
differential preferences for short-term mating. The average number of
short-term mating experiences was higher among heterosexual men
(\emph{M} = 3.78, \emph{SD} = 0.50) than among heterosexual women
(\emph{M} = 2.79, \emph{SD} = 0.35), \emph{t}(4,998) = -81.53, \emph{p}
\textless{} .001, Cohen's \emph{d} = 2.31. Likewise, the average number
of short-term mates was higher among heterosexual men (\emph{M} = 2.12,
\emph{SD} = 0.17) than among heterosexual women (\emph{M} = 1.56,
\emph{SD} = 0.11), \emph{t}(4,998) = -135.85, \emph{p} \textless{} .001,
Cohen's \emph{d} = 3.84.

@@

Gay men engaged in short-term mating behaviors more than heterosexual
men did (Figure 2). The average number of short-term mating experiences
(as calculated using the full population of men) was higher among gay
men (\emph{M} = 2.63, \emph{SD} = 0.37) than among heterosexual men
(\emph{M} = 1.43, \emph{SD} = 0.24), \emph{t}(4,998) = -134.87, \emph{p}
\textless{} .001, Cohen's \emph{d} = 3.81. Similarly, the average number
of short-term mates (as calculated using the full population of men) was
higher among gay men (\emph{M} = 1.72, \emph{SD} = 0.19) than among
heterosexual men (\emph{M} = 0.80, \emph{SD} = 0.11), \emph{t}(4,998) =
-206.91, \emph{p} \textless{} .001, Cohen's \emph{d} = 5.85.

\begin{figure}[h]
  \centering
  \includegraphics[width=0.8\columnwidth]{figures/fig2_hetero_vs_gay_men.pdf}
  \caption{\textbf{Short-term mating behaviors of heterosexual and gay men after 1,000 time steps in the model when gender differences existed in mating preferences.} Violin plots summarizing the outcome variables. Plot (A) shows the average number of short-term mating experiences, and plot (B) shows the average number of short-term mates. Central points show mean values and whiskers represent standard errors, but the standard errors are small and overlap to form a single bar. The averages were calculated using the full population of heterosexual and gay men in the model (\textit{N\textsubscript{hetero}} = \textit{N\textsubscript{gay}} = 150).}
\end{figure}

>>>>

The results from Experiment 1 showed that when there were gender
differences in preferences for short-term mating, there was no gender
difference in the average number of short-term mating experiences among
the full population of heterosexual individuals
(\emph{M\textsubscript{men}} = 1.43, \emph{SD\textsubscript{men}} =
0.24; \emph{M\textsubscript{women}} = 1.43,
\emph{SD\textsubscript{women}} = 0.24), Cohen's \emph{d} = 0.00. Nor was
there a difference in the average number of short-term mates
(\emph{M\textsubscript{men}} = 0.80, \emph{SD\textsubscript{men}} =
0.11; \emph{M\textsubscript{women}} = 0.80,
\emph{SD\textsubscript{women}} = 0.11), Cohen's \emph{d} = 0.00 (Figure
\ref{fig:men_vs_women}).

\begin{figure}[h]
  \centering
  \includegraphics[width=100mm]{figures/fig1_men_vs_women.pdf}
  \caption{\textbf{Short-term mating behaviors of men and women after 1,000 time steps in the model when gender differences existed in mating preferences.} Violin plots summarizing the outcome variables separately for heterosexual individuals and gay men and lesbian women. Plot (A) shows the average number of short-term mating experiences, and plot (B) shows the average number of short-term mates. Central points show mean values and whiskers represent standard errors, but the standard errors are small and overlap to form a single bar. The averages were calculated using the full population of men and women in the model (\textit{N\textsubscript{men}} = \textit{N\textsubscript{women}} = 150).}
  \label{fig:men_vs_women}
\end{figure}

The results from Experiment 2 showed that when there were gender
differences in preferences for short-term mating, there were gender
differences in short-term mating behaviors between gay men and lesbian
women (Figure \ref{fig:men_vs_women}). The average number of short-term
mating experiences was higher among gay men (\emph{M} = 2.63, \emph{SD}
= 0.37) than among lesbian women (\emph{M} = 0.32, \emph{SD} = 0.10),
\emph{t}(4,998) = -301.78, \emph{p} \textless{} .001, Cohen's \emph{d} =
8.54. Similarly, the average number of short-term mates was higher among
gay men (\emph{M} = 1.72, \emph{SD} = 0.19) than among lesbian women
(\emph{M} = 0.25, \emph{SD} = 0.07), \emph{t}(4,998) = -357.69, \emph{p}
\textless{} .001, Cohen's \emph{d} = 10.12.

@@

In Experiment 1, there was a smaller proportion of heterosexual men in
the mating pool (\emph{M} = 0.38, \emph{SD} = 0.04) compared to women
(\emph{M} = 0.51, \emph{SD} = 0.05)), \emph{t}(4,998) = 104.85, \emph{p}
\textless{} .001, Cohen's \emph{d} = 2.97. In this population, there
were gender differences in short-term mating behaviors when men and
women had differential preferences for short-term mating (Figure
\textbf{x}). The average number of short-term mating experiences was
higher among heterosexual men (\emph{M} = 3.78, \emph{SD} = 0.50) than
among heterosexual women (\emph{M} = 2.79, \emph{SD} = 0.35),
\emph{t}(4,998) = -81.53, \emph{p} \textless{} .001, Cohen's \emph{d} =
2.31. Likewise, the average number of short-term mates was higher among
heterosexual men (\emph{M} = 2.12, \emph{SD} = 0.17) than among
heterosexual women (\emph{M} = 1.56, \emph{SD} = 0.11), \emph{t}(4,998)
= -135.85, \emph{p} \textless{} .001, Cohen's \emph{d} = 3.84.

@@

Gay men engaged in short-term mating behaviors more than heterosexual
men did (Figure \ref{fig:hetero_vs_gay}). The average number of
short-term mating experiences (as calculated using the full population
of men) was higher among gay men (\emph{M} = 2.63, \emph{SD} = 0.37)
than among heterosexual men (\emph{M} = 1.43, \emph{SD} = 0.24),
\emph{t}(4,998) = -134.87, \emph{p} \textless{} .001, Cohen's \emph{d} =
3.81. Similarly, the average number of short-term mates (as calculated
using the full population of men) was higher among gay men (\emph{M} =
1.72, \emph{SD} = 0.19) than among heterosexual men (\emph{M} = 0.80,
\emph{SD} = 0.11), \emph{t}(4,998) = -206.91, \emph{p} \textless{} .001,
Cohen's \emph{d} = 5.85.

\begin{figure}[h]
  \centering
  \includegraphics[width=0.8\columnwidth]{figures/fig3_hetero_vs_gay_men.pdf}
  \caption{\textbf{Short-term mating behaviors of heterosexual and gay men after 1,000 time steps in the model when gender differences existed in mating preferences.} Violin plots summarizing the outcome variables. Plot (A) shows the average number of short-term mating experiences, and plot (B) shows the average number of short-term mates. Central points show mean values and whiskers represent standard errors, but the standard errors are small and overlap to form a single bar. The averages were calculated using the full population of heterosexual and gay men in the model (\textit{N\textsubscript{hetero}} = \textit{N\textsubscript{gay}} = 150).}
  \label{fig:hetero_vs_gay}
\end{figure}
